Project 2

### 2018-09-30 Project2/report/Project2.tex
Adding plots
End of one e

\subsection{Quantum dots, one electron}
The method derived in the section for the buckling beam is general for a problem that can be described by a differential equation on the form of \eqref{eq:du/dx=lambda}. The method can be extended to a quantum mechanical problem, if the problem can be transformed into a differential equation as mentioned. The radial part of the Schr$\ddot{\mathrm{o}}$dinger equation with the orbital angular momentum number $l = 0$ is
%
\begin{equation*}
    -\frac{\hbar^2}{2m}\left(\frac{1}{r^2}\frac{d}{dr}r^2\frac{d}{dr}\right)R(r) + V(r)R(r) = ER(r),
\end{equation*}
%
where $r \in [0,\infty)$, the potential $V(r)$ is the harmonic oscillator potential $V(r) = (1/2)kr^2$, where $k = mw^2$ and $\omega$ is the oscillator frequency. The allowed energies are 
%
\begin{equation*}
    E_{n0} = \left(2n + \frac{3}{2}\right),
\end{equation*}
%
for  n = 0, 1, 2,.... Substituting $R(r) = u(r)/r$:
%
\begin{equation*}
    -\frac{\hbar^2}{2m}\frac{1}{r^2}\frac{d}{dr}r^2 \frac{d}{dr}\frac{u(r)}{r} + V(r)\frac{u(r)}{r} = E\frac{u(r)}{r}.
\end{equation*}
%
Evaluating the derivatives in the above equation:
%
\begin{align*}
    \frac{1}{r^2}\frac{d}{dr}r^2\frac{d}{dr}\frac{u(r)}{r} &=  \frac{1}{r^2}\frac{d}{dr}r^2\left(\frac{\frac{du}{dr}r - u}{r^2}\right) \\
    &= \frac{1}{r^2}\frac{d}{dr}\left(\frac{du}{dr}r - u\right) \\
    &= \frac{1}{r^2}\left(\frac{d^2u}{dr^2}r + \frac{du}{dr} - \frac{du}{dr}\right) \\
    &= \frac{1}{r}\frac{d^2u}{dr^2},
\end{align*}
%
Inserting the above and multiplying by r yields
%
\begin{equation*}
    -\frac{\hbar^2}{2m}\frac{d^2u}{dr^2} + V(r)u(r) = Eu(r).
\end{equation*}
%
where the boundary conditions of $u$ are $u(0) = u(\infty) = 0$. Defining a dimensionless variable $\rho = r/\alpha$ transforms the potential to $V(\rho) = (1/2)k\alpha^2\rho^2$, and the Schr$\ddot{\mathrm{o}}$dinger's equation becomes
%
\begin{equation*}
    -\frac{\hbar}{2m\alpha^2}\frac{d^2u(\rho)}{d\rho^2} + \frac{1}{2}k\alpha^2\rho^2u(\rho) = Eu(\rho).
\end{equation*}
%
Multiplying the above equation by $2m\alpha^2 / \hbar^2$
%
\begin{equation*}
    -\frac{d^2u(\rho)}{d\rho^2} + \frac{mk}{\hbar^2}\alpha^2 \rho^2u(\rho) = \frac{2m\alpha^2}{\hbar^2}
\end{equation*}

@@

@@

@@

>>>>

\subsection{Quantum dots, one electron}
The method derived in the section for the buckling beam is general for a problem that can be described by a differential equation on the form of Eq. \eqref{eq:du/dx=lambda}. The method can be extended to a quantum mechanical problem, if the problem can be transformed into a differential equation as mentioned. The radial part of the Schr$\ddot{\mathrm{o}}$dinger equation with the orbital angular momentum number $l = 0$ is
%
\begin{equation*}
    -\frac{\hbar^2}{2m}\left(\frac{1}{r^2}\frac{d}{dr}r^2\frac{d}{dr}\right)R(r) + V(r)R(r) = ER(r),
\end{equation*}
%
where $r \in [0,\infty)$, the potential $V(r)$ is the harmonic oscillator potential $V(r) = (1/2)kr^2$, where $k = mw^2$ and $\omega$ is the oscillator frequency. The allowed energies are 
%
\begin{equation*}
    E_{n0} = \left(2n + \frac{3}{2}\right),
\end{equation*}
%
for  n = 0, 1, 2,.... Substituting $R(r) = u(r)/r$:
%
\begin{equation*}
    -\frac{\hbar^2}{2m}\frac{1}{r^2}\frac{d}{dr}r^2 \frac{d}{dr}\frac{u(r)}{r} + V(r)\frac{u(r)}{r} = E\frac{u(r)}{r}.
\end{equation*}
%
Evaluating the derivatives in the above equation:
%
\begin{align*}
    \frac{1}{r^2}\frac{d}{dr}r^2\frac{d}{dr}\frac{u(r)}{r} &=  \frac{1}{r^2}\frac{d}{dr}r^2\left(\frac{\frac{du}{dr}r - u}{r^2}\right) \\
    &= \frac{1}{r^2}\frac{d}{dr}\left(\frac{du}{dr}r - u\right) \\
    &= \frac{1}{r^2}\left(\frac{d^2u}{dr^2}r + \frac{du}{dr} - \frac{du}{dr}\right) \\
    &= \frac{1}{r}\frac{d^2u}{dr^2},
\end{align*}
%
Inserting the above and multiplying by r yields
%
\begin{equation*}
    -\frac{\hbar^2}{2m}\frac{d^2u}{dr^2} + V(r)u(r) = Eu(r).
\end{equation*}
%
where the boundary conditions of $u$ are $u(0) = u(\infty) = 0$. Defining a dimensionless variable $\rho = r/\alpha$ transforms the potential to $V(\rho) = (1/2)k\alpha^2\rho^2$, and the Schr$\ddot{\mathrm{o}}$dinger's equation becomes
%
\begin{equation*}
    -\frac{\hbar}{2m\alpha^2}\frac{d^2u(\rho)}{d\rho^2} + \frac{1}{2}k\alpha^2\rho^2u(\rho) = Eu(\rho).
\end{equation*}
%
Multiplying the above equation by $2m\alpha^2 / \hbar^2$
%
\begin{equation*}
    -\frac{d^2u(\rho)}{d\rho^2} + \frac{mk}{\hbar^2}\alpha^4 \rho^2u(\rho) = \frac{2m\alpha^2}{\hbar^2}Eu(\rho).
\end{equation*}
%
Where the factor in front of $u(\rho$ on the right hand side is defined as
%
\begin{equation*}
    \lambda = \frac{2m\alpha^2}{\hbar^2}E,
\end{equation*}
%
which corresponds to the eigenvalues of the problem. To transform the equation to a form such that it can be solved as an eigenvalue problem, $\alpha$ is fixed such that
%
\begin{equation*}
    \frac{mk}{\hbar^2}\alpha^4 = 1
    \Rightarrow \alpha = \left(\frac{\hbar^2}{mk}\right)^{1/4}.
\end{equation*}
%
The rewritten expression for the Schr$\ddot{\mathrm{o}}$dinger equation is then
%
\begin{equation*}
    -\frac{d^2}{d\rho^2}u(\rho) + \rho^2u(\rho) = \lambda u(\rho),
\end{equation*}
%
which has known analytical eigenvalues for the ground state (with $l=0)$ $\lambda_{n=0} = 3$ and for the two first excited states $\lambda_1 = 7, \lambda_2 = 11$.

@@

\begin{figure}[t]
\mbox{\epsfig{figure=iterationspersize.pdf,width=\linewidth,clip=}}
\caption{Logarithmic plot of }
\label{fig:fig1}
\end{figure}

@@

\begin{figure}[t]
\mbox{\epsfig{figure=GSEperOMGr.pdf,width=\linewidth,clip=}}
\caption{}
\label{fig:fig2}
\end{figure}

@@

\begin{figure}[t]
\mbox{\epsfig{figure=ProbfuncperRhon.pdf,width=\linewidth,clip=}}
\caption{Logarithmic plot of }
\label{fig:fig3}
\end{figure}
